Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-08-11 Report/dual_approach.tex
updated tex

\subsubsection*{Convergence}
The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to the optimal value for a fixed \ac{SCA} point. Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to the optimal value \cite{boyd2011distributed} for a given \ac{SCA} point. The receive beamformers are updated at each \ac{SCA} update provides monotonic increase in the objective function, since the \ac{MMSE} receive beamformers are optimal for the fixed transmit precoders obtained by solving the subproblems until convergence. The algorithmic representation of the \ac{ADMM} based approach for decentralization is given in Algorithm \ref{algo-3}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
 initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
        exchange \me{\mbfa{\zeta}^{\set{b}(j)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
		update the dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update} \;
        update the global interference vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update} \;
		\me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via \ac{ADMM} for \acs{JSFRA} scheme}
  \label{algo-3}
\end{algorithm}

>>>>

\subsubsection*{Convergence}
The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to the optimal value for a fixed \ac{SCA} point. Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to the optimal value \cite{boyd2011distributed} for a given \ac{SCA} point. The receive beamformers are updated at each \ac{SCA} update provides monotonic increase in the objective function, since the \ac{MMSE} receive beamformers are optimal for the fixed transmit precoders obtained by solving the subproblems until convergence. The algorithmic representation of the \ac{ADMM} based approach for decentralization is given in Algorithm \ref{algo-3}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
 initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
        exchange \me{\mbfa{\zeta}^{\set{b}(j)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
		update the dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update} \;
        update the global interference vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update} \;
		\me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} by exchanging the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via \ac{ADMM} for \acs{JSFRA} scheme}
  \label{algo-3}
\end{algorithm}

### 2014-08-11 Report/primal_approach_appendix.tex
Corrections after first reading
updated tex

By fixing the interference values \me{\zeta_{\pr{l},\pr{k},n,{b_k}}} corresponding to the interference from the \ac{BS} \me{b_k}, the constraint involving the coupling variables \eqref{eqn-9.1c} can be relaxed using the equivalent formulation in \eqref{eqn-decent-3}. Now, the subproblem for the \ac{BS} \me{b_k \in \mc{B}} can be obtained by grouping the terms relevant to the \ac{BS} \me{b_k} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
\text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\
&& \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-primal-1d} \\
&& \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\
 & \quad & \text{and} \; \eqref{eqn-8} \IEEEyessubnumber,
\end{IEEEeqnarray}

@@

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via Primal Decomposition for \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

>>>>

By fixing the interference values \me{\zeta_{\pr{l},\pr{k},n,{b_k}}} corresponding to the interference from the \ac{BS} \me{b_k}, the constraint involving the coupling variables \eqref{eqn-9.1c} can be relaxed using the equivalent formulation in \eqref{eqn-decent-3}. Now, the subproblem for the \ac{BS} \me{b_k \in \mc{B}} can be obtained by grouping the terms relevant to the \ac{BS} \me{b_k} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n} \\ \mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
\text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\
&& \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-primal-1d} \\
&& \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\
 & \quad & \text{and} \; \eqref{eqn-8} \IEEEyessubnumber,
\end{IEEEeqnarray}

@@

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} by exchanging the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via Primal Decomposition for \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

### 2014-08-11 Report/simulation_distributed.tex
updated tex

The performance of the \ac{MSE}-\ac{KKT} scheme discussed in Section \ref{sec-4.3} is presented in Fig. \ref{fig-d-3}. It compares the \ac{JSFRA} scheme with \me{\ell_1} and \me{\ell_2} norm cases in addition to the \ac{Q-WSRM} scheme. We compare the performance of the \ac{MSE}-\ac{KKT} scheme for the exponents \me{q=1} and \me{q=2}. The performance of the \me{\ell_1} \ac{JSFRA} scheme performs the best over other algorithms in minimizing the total number of queued bits after the current allocation due to the greedy approach of the objective. The inclusion of the additional second order rate term in \eqref{pf-1}, the \me{\ell_2} \ac{JSFRA} scheme achieves different performance than the \ac{Q-WSRM} scheme as shown in Fig. \ref{fig-d-3}.

It can be seen from Fig. \ref{fig-d-3.2}, that the sum rate of the \me{q=1} \ac{KKT} approach outperforms other schemes in spite of Fig. \ref{fig-d-3.1} showing inferior queue minimizing performance. This due to the lack of the rate bounding constraint \eqref{kkt-mse-4.2}, which is simply given by \me{\sigma_{l,k,n}^{(i)} = \frac{a_k}{\log(2)}}, providing no control for the excess allocations. For \me{q=2}, when the allocated rate exceeds the available queued bits, \me{\sigma_{l,k,n}^{(i)}} will be negative, thereby reducing \eqref{kkt-mse-4.1} as \me{\alpha_{l,k,n}^{(i)} < \alpha_{l,k,n}^{(i-1)}} to reduce the priority for the corresponding user in the next iteration. The performance of the closed form solution using the \ac{KKT} solution performs similar to the centralized schemes with \me{q=2} by limiting the rates beyond the available queued packets.
\begin{figure*}
\centering
\subfloat[][Queue deviation]{
\includegraphics[width=0.48\textwidth]{fig-9-2}
\label{fig-d-3.1}}
\hfill
\subfloat[][Sum rate performance]{
\includegraphics[width=0.48\textwidth]{fig-10}
\label{fig-d-3.2}}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

>>>>

Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method is not converged to the optimal point but oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure*}
\centering
\subfloat[][Queue deviation]{
\includegraphics[width=0.48\textwidth]{fig-9-2}
\label{fig-d-3.1}}
\hfill
\subfloat[][Sum rate performance]{
\includegraphics[width=0.48\textwidth]{fig-10}
\label{fig-d-3.2}}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot. The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables are not allowed to converge in between the \ac{SCA} steps in the \ac{KKT} approach. In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}. The figure compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRM} scheme compared to the \me{\ell_2} norm which includes it. By dropping the squared rate variable, the \ac{Q-WSRM} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues. Contrastingly, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-08-11 Report/simulation_results.tex
updated tex

In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently. In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels. At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders. The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig. \ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips. Fig. \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
%\begin{table}
%\centering
%\renewcommand{\arraystretch}{1.25} \scriptsize
%\begin{tabular}{|c|*{8}{c}|c|}
%\hline
%\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
%\hline
%\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
%\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
%\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
%\hline
%\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
%\cline{1-9}
%\end{tabular}
%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
%\label{tbl-3}
%\end{table}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{tbl-2}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{figure}

The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Fig. \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas. The configuration is mentioned in the caption of Fig. \ref{tbl-3} along with the number of queued bits for each user. It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits. The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets \me{\chi_k = 3.58} bits. The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.

>>>>

In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently. In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels. At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders. The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig. \ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips. Fig. \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas. In this setup, we assume the queue sizes of the users are small enough to bring out the difference between the receiver performances for the \ac{JSFRA} solution discussed in Section \ref{sec-3.2.1}. In this scenario, the performance of the \ac{MMSE} receiver is not the same as the optimal receiver when the objective is not equivalent to the \ac{WSRM} approach.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
\hline
\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
\cline{1-9}
\end{tabular}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{table}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-2}
%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
%\label{tbl-3}
%\end{figure}

The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table. \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas. The configuration is mentioned in the caption of Table. \ref{tbl-3} along with the number of queued bits for each user. It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits. The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets \me{\chi_k = 3.58} bits. The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.
